Accurate plant pathogen effector protein classification _ab initio_ with **deepredeff**, an ensemble of convolutional neural networks.

### 2020-06-10 main.Rmd
Added the acc, f1-score table and plot of conf_mat from classification result using effectR reference sequences in main.Rmd

@@

```{r effectorpdatacfmat, fig.width=6, fig.height=6, fig.cap="Confusion matrices of classifications made by our fungi model compared with EffectorP 1.0 and EffectorP 2.0 evaluated on both training and validation EffectorP data.", fig.pos="H"}

@@

```{r effectivet3datacfmat, fig.width=6, fig.height=3, fig.cap="Confusion matrices of classifications made by our bacteria model compared with both EffectiveT3 based on plant associated and all protein evaluated on positive EffectiveT3 data.", fig.pos="H"}

@@

>>>>

```{r accf1scoreeffectRdata}
apa_table(
  readr::read_csv("data/processed/acc_f1_score_effectR_data_prediction.csv"),
  digits = 4,
  align = 'c',
  caption = 'Accuracy and F1-Score from prediction results of reference sequences of EffectR evaluated on our model and EffectR.',
  placement = "H"
)
```

@@

```{r effectorpdatacfmat, fig.width=6, fig.height=6, fig.cap="Confusion matrices of classifications made by our fungi model compared with EffectorP 1.0 and EffectorP 2.0 evaluated on both training and validation EffectorP data.", fig.pos="H", message=FALSE}

@@

```{r effectivet3datacfmat, fig.width=6, fig.height=3, fig.cap="Confusion matrices of classifications made by our bacteria model compared with both EffectiveT3 based on plant associated and all protein evaluated on positive EffectiveT3 data.", fig.pos="H", message=FALSE}

@@

```{r effectRdatacfmat, fig.width=6, fig.height=3, fig.cap="Confusion matrices of classifications made by our bacteria model compared with both EffectiveT3 based on plant associated and all protein evaluated on positive EffectiveT3 data.", fig.pos="H", message=FALSE}

readr::read_csv("data/processed/conf_mat_effectR_data_prediction.csv") %>% 
  dplyr::mutate(
  tool = factor(tool, levels = c("cnn_lstm", "effectR"))
  ) %>% 
  ggplot2::ggplot() +
  ggplot2::aes(x = Truth, y = Prediction) +
  ggplot2::geom_tile(ggplot2::aes(fill = Freq), colour = "white") +
  ggplot2::geom_text(ggplot2::aes(label = Freq), vjust = 0.5) +
  ggplot2::facet_grid(~tool) +
  ggplot2::scale_fill_viridis_c(begin = 0.2, end = 1) +
  ggplot2::labs(x = "True value", y = "Prediction") +
  ggplot2::coord_fixed()
```
